### 2017-08-08 Paper01_EnthalpyAndCrystallization.tex
Results - Decon - Tx Onsets - Started draft section paragraphs

Both the bulk and film \MgZnCa~ were examined at various \acrshort{dsc} heating rates to observe changed in the \Tg and \Tx temperatures. As expected higher heating rates resulted endothermic peaks shifting to higher temperatures and curve convolution.

Numerical solutions were used to deconvolution the \acrshort{dsc} data so the various \Tx onsets could be determined. The results of the deconvolution are presented in Table \ref{tab:BulkOnsets} for the bulk and Table \ref{tab:FilmOnsets} for the film.

>>>>

Numerical solutions were used to deconvolute the isochronic \acrshort{dsc} data so the various \Tx~ onsets could be accurately determined. This numerical fitting utilised a summation of skewed Gaussian curves to fit a target curve corresponding to the original \acrshort{dsc} \glspl{ht} for both the bulk and film, see Figures \ref{fig:DSC_Bulk_Decon} and \ref{fig:DSC_Film_Decon}. Similar solutions to \acrshort{dsc} deconvolution \cite{

The results of the deconvolution are presented in Table \ref{tab:BulkOnsets} for the bulk and Table \ref{tab:FilmOnsets} for the film. Note \Tg~ and \Tx$_{1}$ are not obtained from the deconvolution.
